\chapter*{Acknowledgment}
\thispagestyle{empty}
This work is funded by the \textit{Consejo Nacional de Ciencia y Tecnologia -- CONACYT} (the Mexican National Council for Science and Technology).

I would like to thank Prof. Dr. Alberto Garc\'ia-Ortiz, my Ph.D. supervisor, for his invaluable help in this process. He encouraged me when I underestimated my work and he criticized me when I overestimated it. He knows how to raise students to the level of independent researchers. I would also like to thank Prof. Dr. X for his guidance and for his time to review this work. Moreover, I would like to thank the members of the graduation committee for their review and suggestions. I would like to thank Mexico and Conacyt for financially supporting my PhD. Special thanks to Tovalin, Julian Rosales, Fernando De la Torre, Ulises Ponce, Carlos Cruz, and Kai M\"uller for their inspiration for teaching.

I would also like to thank my colleagues Ardalan Najafi, Amir Najafi, Wanli Yu, Yanqiu Huang, Robert Schmidt, Yizhi Chen, Jinming Sun, and Andreas Beering. They are excellent human beans, professional, supportive, and brilliant minds. I also want to thank David Rotermund and Klaus Pawelzik (Institute for Theoretical Physics, University of Bremen) for their collaboration and guidance. A special thanks to all the students I have supervised during my Ph.D. for helping me understand life better. I would like to thank Kerstin Janssen and Peter Lutzen for their support in the research department. I would also like to thank the University of Bremen and the Studierendenwerk for providing the organization and facilities. I am sure that it would not be possible to reach this point without your kind support.


I would like to thank Atena Berhang, my life-partner, and her family for their sweet and constant support. Likewise, I want to thank my parents for their effort and encouragement to practice virtue, universal love, fraternity, brotherhood, and morality since my childhood. I want to thank my brothers Kevin and Efren, great sages, my best friends. I also thank other family and friends for their support and good wishes during my doctorate.

I would like to thank Marcus Aurelius, Epictetus, Seneca, and Nezahualc\'oyotl for their meditations, thoughts, poems, and mentorship.


Yarib Nevarez

Bremen, May 2022.




